Appendix S2: Data Exploration

### 2022-03-11 ms/data_exploration.Rmd
Update data exploration (SI2)

* `grids`: ID code for each grid cell
* `lat`: latitude of grid cell centroid
* `long`: longitude of grid cell centroid
* `richness`: number of taxa
* `pd_obs_z`: standard effect size (SES) of phylogenetic diversity (pd)
* `fd_obs_z`: SES of functional diversity (fd)
* `rpd_obs_z`: SES of relative pd
* `rfd_obs_z`: SES of relative fd
* `percent_apo`: percent of apogamous taxa in that grid cell
* `temp`: mean annual temperature (10 x °C)
* `precip`: total annual precipitation (mm)
* `precip_season`: seasonality in precipitation
* `lat_area`: rolling mean of area in 0.2 degree latitudinal bands

@@

Grubb's test confirms that the percent apomictic value is an outlier. It also indicates that the highest values of the variables `fd_obs_z`, `pd_obs_z`, `rfd_obs_z`, and `rpd_obs_z` may be outliers.

>>>>

* `grids`: ID code for each grid cell
* `lat`: latitude of grid cell centroid
* `long`: longitude of grid cell centroid
* `richness`: number of taxa
* `pd_obs_z`: standard effect size (SES) of phylogenetic diversity (pd)
* `fd_obs_z`: SES of functional diversity (fd)
* `rpd_obs_z`: SES of relative pd
* `rfd_obs_z`: SES of relative fd
* `percent_apo`: percent of apogamous taxa in that grid cell
* `temp`: mean annual temperature (10 x °C)
* `precip`: total annual precipitation (mm)
* `precip_season`: seasonality in precipitation
* `lat_area`: rolling mean of area in 100 km latitudinal bands

@@

Grubb's test confirms that the percent apomictic value is an outlier. It also indicates that the highest values of the variables `pd_obs_z`, `fd_obs_z`, `rpd_obs_z`, and `rfd_obs_z` may be outliers.
